---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tibbleOne

The goal of `tibbleOne` is to make it easy for analysts to include a Table 1 object in both LaTeX and html markdown documents. I made this package because I was unable to get the html tables I wanted from the existing table one R packages. Notably, this package has far fewer features than the outstanding TableOne package, but it can get a readable Table 1 object into a markdown document with less effort.

## Installation

You can install the latest version of tibbleOne from github with:

``` r
devtools::install_github('bcjaeger/tibbleOne')
```

## Example

For a more detailed example, see the 'start here' vignette. This example shows basic elements of `tibbleOne`.

```{r example, message = FALSE}

library(knitr)
library(kableExtra)
library(tibbleOne)
library(tidyverse)

```

The first step should be setting labels for variables that will be in the table. This can be done using `set_variable_labels` and then building a `meta` data set. You may also just pipe the labelled dataset into `tibble_one()`, but it is generally more useful to keep the `meta` data object in case you need to use the labels for other tables in your analysis. 

```{r}

meta <- pbc_tbl1 %>% 
  set_variable_labels(
    status = "Status at last contact",
    trt = "Treatment group",
    age = 'Age',
    sex = 'Sex at birth',
    ascites = 'Ascites',
    bili = 'Bilirubin levels',
    edema = 'Edema',
    albumin = 'Serum Albumin'
  ) %>%
  build_meta()

tbl_one <- tibble_one(
  data = pbc_tbl1,
  meta_data = meta,
  formula = ~ . | trt,
  include_pval = TRUE
)

```

Last step, we pass `tbl_one` into the `to_kable()` function, which provides a couple of nice formatting procedures to make the data look like the type of Table 1 that you may see in a published article.

```{r}

cap <- 'Characteristics of patients with primary biliarry cirrhosis.'

tbl_one %>% 
  to_kable(caption = cap) %>%
  kable_styling(
    position = 'center',
    bootstrap_options = c('striped')
  )

```
